% ======================================================================
% sections/back_matter.tex
%
% Back matter for the paper:
%   Triple Humanoid 24/7 Adverse Event Oncology Trial Response Team:
%   4-Site Rotation
%
% This file holds the Acknowledgments, Ethical Disclosures, Rights and
% Permissions, Cite This Article, and Data Availability sections, in
% that order. The text below is final-form text. A future Claude Code
% Opus 4.7 1M Max session should keep this content and only update the
% DOI placeholder when the Zenodo record is minted.
% ======================================================================

\phantomsection
\addcontentsline{toc}{section}{Acknowledgments}
\section*{Acknowledgments}

The author would like to acknowledge Anthropic for providing access to
Claude Code for instruction, code, execution, along with the paper
generation process; OpenAI for providing access to ChatGPT for deep
research summaries, and Google Gemini AI Overview for additional
search assistance.

\phantomsection
\addcontentsline{toc}{section}{Ethical Disclosures}
\section*{Ethical Disclosures}

The author of the article declares no competing interests.

\phantomsection
\addcontentsline{toc}{section}{Rights and Permissions}
\section*{Rights and Permissions}

This article is distributed under the terms of the Creative Commons
Attribution 4.0 International License (CC BY 4.0), which permits
unrestricted use, distribution, and reproduction in any medium,
provided the original author(s) and source are properly credited, a
link to the Creative Commons license is provided, and any
modifications made are indicated. To view a copy of this license,
visit \href{https://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.

\phantomsection
\addcontentsline{toc}{section}{Cite This Article}
\section*{Cite This Article}

Kawchak K. Triple Humanoid 24/7 Adverse Event Oncology Trial Response
Team: 4-Site Rotation. Zenodo. 2026; \href{https://doi.org/10.5281/zenodo.xxxxxxxx}{10.5281/zenodo.xxxxxxxx}.

\phantomsection
\addcontentsline{toc}{section}{Data Availability}
\section*{Data Availability}

[DATA AVAILABILITY INSTRUCTIONS FOR FUTURE CLAUDE CODE OPUS 4.7 1M
MAX SESSION. Write 1 paragraph that points the reader at the exact
repository directories where the data, code, schemas, configs, and
reports live. Use the file paths below. Do not omit any of them.

\begin{itemize}
  \item Source code: \path{demo-projects/07-humanoid/paper/codegen/src/}
        (27 files spanning Python, C++, Rust, YAML, and Markdown).
  \item Tests: \path{demo-projects/07-humanoid/paper/codegen/tests/}
        (notably \path{test_xyz_safety.py}).
  \item Schemas: \path{demo-projects/07-humanoid/paper/codegen/schemas/}.
  \item Configs: \path{demo-projects/07-humanoid/paper/codegen/config/}.
  \item Data: \path{demo-projects/07-humanoid/paper/codegen/data/}
        and \path{demo-projects/07-humanoid/paper/execution/data/}.
        The iteration index lives at
        \path{codegen/data/iterations/index.jsonl}. The DuckDB
        aggregate lives at
        \path{execution/data/iterations_aggregate.duckdb}. The
        per-site decision streams live in
        \path{execution/data/site_runtime_runs/} as
        \path{AT-01_llm_decisions.jsonl},
        \path{BO-01_llm_decisions.jsonl},
        \path{SD-01_llm_decisions.jsonl}, and
        \path{SF-01_llm_decisions.jsonl}.
  \item Reports: \path{demo-projects/07-humanoid/paper/codegen/reports/}
        and \path{demo-projects/07-humanoid/paper/execution/reports/}.
        The interpretability dashboard lives at
        \path{codegen/reports/dashboard.html}.
  \item ASCII diagrams:
        \path{demo-projects/07-humanoid/paper/codegen/diagrams/}
        and
        \path{demo-projects/07-humanoid/paper/execution/diagrams/}.
  \item Figures: \path{demo-projects/07-humanoid/paper/execution/figures/}
        (6 PNGs at 300 dpi).
  \item Instructions tree:
        \path{demo-projects/07-humanoid/paper/instructions/}
        with subdirectories \path{00-project-overview/} through
        \path{09-runtime-instructions/}.
  \item Prior paper inputs:
        \path{demo-projects/07-humanoid/paper/inputs/} including
        \path{Deep-Research-A/} and \path{Deep-Research-B/}.
  \item Companion repository:
        \path{https://github.com/kevinkawchak/physical-ai-oncology-trials},
        with hours 00 through 55 of
        \path{new-trial/national-24-7-trial/} included as input
        and hours 56 through 83 excluded per the instructions
        README.
\end{itemize}

Close the paragraph by linking to the project DOI placeholder
\path{https://doi.org/10.5281/zenodo.xxxxxxxx} and to the
instructions DOI \path{https://doi.org/10.5281/zenodo.18445179}.]

The data availability statement will name every codegen, execution,
instruction, and input directory so the reader can navigate to the
exact source of every claim in the paper, and will link the project
DOI placeholder and the instructions DOI in a single closing
sentence.

\sectiontable{Back matter disclosure matrix}{%
Acks & B1 & 1 & Anthr, OAI, Goog & Record & Ack block & AI disclosure & Ready \\
Ethics & B2 & 2 & Author & No competing interest & Ethical block & Single sentence & Ready \\
Rights & B3 & 3 & CC BY 4.0 & License terms & Permissions block & License link & Ready \\
Cite & B4 & 4 & DOI placeholder & Suggested citation & Cite block & DOI link & Ready \\
Data & B5 & 5 & Whole paper tree & Per directory pointer & Data block & 9 dirs named & Ready \\
}
