% ======================================================================
% sections/back_matter.tex
%
% Back matter for the full paper:
%   Triple Humanoid 24/7 Adverse Event Oncology Trial Response Team:
%   4-Site Rotation (v0.7.0)
%
% Acknowledgments, Ethical Disclosures, Rights and Permissions, Cite
% This Article, and Data Availability blocks, in that order.
% ======================================================================

\phantomsection
\addcontentsline{toc}{section}{Acknowledgments}
\section*{Acknowledgments}

The author would like to acknowledge Anthropic for providing access
to Claude Code for instruction, code generation, execution, and the
paper draft and full paper passes; OpenAI for providing access to
ChatGPT for deep research summaries; and Google for Google Gemini AI
Overview for additional search assistance.

\phantomsection
\addcontentsline{toc}{section}{Ethical Disclosures}
\section*{Ethical Disclosures}

The author of the article declares no competing interests. The work
is independent and is not endorsed or sponsored by trial sponsors,
the FDA, a contract research organization, a site, an IRB, a
regulator, or a medical society. No real patient data is included.
Patient identifiers throughout the codegen and execution trees are
synthetic and have the form \fp{PAT-NET-001-PNNN}.

\phantomsection
\addcontentsline{toc}{section}{Rights and Permissions}
\section*{Rights and Permissions}

This article is distributed under the terms of the Creative Commons
Attribution 4.0 International License (CC BY 4.0)
\cite{ccby40}, which permits unrestricted use, distribution, and
reproduction in any medium, provided the original author and source
are properly credited, a link to the Creative Commons license is
provided, and any modifications made are indicated. To view a copy
of this license, visit
\href{https://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.

\phantomsection
\addcontentsline{toc}{section}{Cite This Article}
\section*{Cite This Article}

Kawchak K. Triple Humanoid 24/7 Adverse Event Oncology Trial
Response Team: 4-Site Rotation. Zenodo. 2026;
\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{10.5281/zenodo.xxxxxxxx}.

\phantomsection
\addcontentsline{toc}{section}{Data Availability}
\section*{Data Availability}

All source code, schemas, configs, data artifacts, ASCII diagrams,
figures, reports, output tables, and per-step execution logs that
underpin this paper are available in the project repository
\cite{kawchak_2026_clinical_ai_demos_repo}. Table
\ref{tbl:data-availability} pulls the per directory pointers into a
single reader friendly view so a reader can navigate from any claim
in the paper to the exact source of the claim.

\begin{table}[H]
\captionsetup{type=table}
\caption{Data availability pointers. Every directory in the codegen,
execution, instructions, and inputs trees is named so a reader can
navigate from any claim in this paper to the exact source.}
\label{tbl:data-availability}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{4.5cm}
                >{\raggedright\arraybackslash}p{10.5cm}}
\toprule
\textbf{Asset} & \textbf{Location} \\
\midrule
Source code & \fp{paper/codegen/src/} with 27 files spanning Python, C++, Rust, YAML, and Markdown. \\
Tests & \fp{paper/codegen/tests/} with the test of xyz safety and 5 other modules. \\
Schemas & \fp{paper/codegen/schemas/} with 11 JSON Schema files. \\
Configs & \fp{paper/codegen/config/} with 7 YAML config files. \\
Iteration index & \fp{paper/codegen/data/iterations/index.jsonl} with 32 rows. \\
DuckDB aggregate & \fp{paper/execution/data/iterations_aggregate.duckdb}. \\
Per site decision streams & \fp{paper/execution/data/site_runtime_runs/} with 4 jsonl files (SF-01, SD-01, BO-01, AT-01). \\
Reports & \fp{paper/codegen/reports/} and \fp{paper/execution/reports/}. \\
Dashboard & \fp{paper/codegen/reports/dashboard.html}. \\
ASCII diagrams & \fp{paper/codegen/diagrams/} (3 files) and \fp{paper/execution/diagrams/} (4 files). \\
Figures & \fp{paper/execution/figures/} with 6 PNGs at 300 dpi. \\
Instructions tree & \fp{paper/instructions/} with 10 numbered subdirectories. \\
Prior paper inputs & \fp{paper/inputs/} including Deep-Research-A and Deep-Research-B. \\
Companion repo & \url{https://github.com/kevinkawchak/physical-ai-oncology-trials} with hours 00 through 55 of the 24/7 trial. \\
Project Zenodo DOI placeholder & \url{https://doi.org/10.5281/zenodo.xxxxxxxx}. \\
Instructions DOI & \url{https://doi.org/10.5281/zenodo.18445179}. \\
Prior FDA AERS DOI & \url{https://doi.org/10.5281/zenodo.18029100}. \\
\bottomrule
\end{tabular}
\end{table}
